Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-19 cloneoverflow-latex/cloneoverflow.tex
Worked on all the FIXMEs and fixed the confusions of the irrelevant methods filter.

\begin{table}
	\centering
	\caption{Configurations of Simian and NiCad}
	\label{t:param_tuning}
%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{p{0.7cm}|p{2.4cm}|p{3.5cm}}
		\hline 
		Tool & Default (\textit{D}) & EvaClone (\textit{E}) \\
		\hline
		Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, \newline ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\ 
		\hline 
		NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=1000 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming,\newline literal abstraction \\
		\hline
	\end{tabular} %
%}
\end{table}

@@

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-6}
		& & \textit{L} & \textit{S} & \textit{M} & \textit{G} & \\
		\hline 
		%		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
		%		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & \checkmark & \checkmark & 88 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
%		\hline
%		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
		\hline
		\multicolumn{7}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{M}=irr.~methods, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
	\end{tabular} %
	%}
\end{table}

@@

Even choosing only the default configurations, the number of disagreed
clone pair candidates is still too large for manual inspection (67,570
for $S_D$ and 632,855 pairs for $N_D$). We applied four filters: clone
size, irrelevant methods, similarity threshold, and good/ok pairs. For
the \emph{clone size filter}, we raised the minimum clone size to 10 lines
since larger clones are more interesting, while smaller ones tend to
be false clones~\cite{Saini2016}.
% Since the 10--line threshold is already the default configuration for
% NiCad, this filter is applied to Simian only (Simian's default
% configuration has a minimum clone size of 6 lines).
The \emph{irrelevant methods filter} removes clones of
\verb|hashCode()| methods and getters/setters which are almost always
false clones. The third filter, \emph{similarity threshold}, applies
only to NiCad clone pairs since Simian does not provide a similarity
configuration. The last filter, \emph{good/ok pairs}, removes the
clone pairs that already exist in the agreed clone sets.

As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the
results using clone size, irrelevant methods, and gook/ok pairs. The
three filters reduced the number of $S_D$ clones to 17,801 pairs.  We
filtered $N_D$ clones by additionally raising the similarity
threshold. We increased NiCad's similarity threshold from 70\% to 85\%
(by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15). We
tried varying the UPI from 70\% (default, 632,855 pairs), 80\%
(25,003 pairs), 85\% (185 pairs) and 90\% (83 pairs) and found that
85\% similarity provided the best balance in terms of the amount of
reported clones and precision for small clones. Using this filter
along with the other three filters, we reduced the number of $N_D$
clones to 88 pairs.

@@

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations.

\FIXME{Can you say something about the numbers only looking at the set
  of pairs used for manual inspection?}
% FIXME
% However, as it is well known that the precision of clone detectors is
c% not very good, it is clear that the above numbers may not be
% representative for real code clones and we ...

@@

\FIXME{Why equals here but not hashcode? Why isn't it the same
  irrelevant methods filter?}

We rely on a manual study to qualitatively investigate the patterns of
online code cloning. To achieve this, we classified all 31,946
selected clone pairs according to the process shown in
\Cref{fig:classification_process}.  Before performing the manual
classification, we used the irrelevant method filter to automatically
classify {\small\texttt{equals()}} and the remaining
getters/setters. As shown in
\Cref{tab:online_clone_classification_results}, the automatic
classifier helped us classified and captured 28,314 clone pairs into
pattern \textbf{BP}.

@@

\begin{table}
	\centering
	\caption{Classifications of online clone pairs. FIXME switch
          UD and EX}
	\label{tab:classification_good_o}
	%\small
	%\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|rrrr|rrr|r}
			\hline
			Set & QS & SQ & UD & EX & BP & IN & AC & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
			\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 20 & 41 & 11,547 & 22 & 105 & 11,749 \\
			\multirow{1}{*}{$S_D'$} & 86 & 0 & 293 & 146 & 17,074 & 74 & 128 & 17,801 \\
			\multirow{1}{*}{$N_D'$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
			\hline
			Total & 112 & 0 & 359 & 197 & 28,749 & 111 & 2,418 & 31,946 \\ 
			\hline
		\end{tabular} 
	%}
\end{table}

@@

\textbf{To answer RQ2, we found that a large amount of the clone pairs
  between Stack Overflow and Qualitas projects are boiler-plate code
  (28,642) or accidental clones (2,525) with no evidence that the code
  has actually been copied. Nevertheless, we found 110 pairs that had
  strong evidences to be cloned from Qualitas to Stack Overflow and
  178 pairs were found to be cloned to Stack Overflow from external
  sources outside Qualitas projects.} 
%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}

@@

\FIXME{You are using the complete number of pairs in a project instead
  of the outdated pairs!!!}
 %Some of the clone pairs overlap with each other so we group them in the same row. 
We discovered 64 outdated online clone pairs out of 112 pairs. As
shown in \Cref{fig:outdated}, \textsf{spring} and \textsf{hibernate}
have the highest number of 20 outdated pairs, followed by 15 from
\textsf{eclipse}, and 12 from \textsf{hadoop}. Besides the example of
outdated code in the \textsf{hadoop}'s
{\small{\texttt{WritableComparator.java}}} shown in
\Cref{fig:before-after}, we also found a few outdated code elements
which contained a large amount of modifications. For example, the code
snippet in Stack Overflow post 23520731 is a copy of
{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code
has been heavily modified on 5 February 2016.

In the 64 outdated pairs, we found 5``dead'' snippets. These snippets
cannot be located in the latest version of the projects. For example,
the snippet in Stack Overflow post 3758110, a copy of
{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in
\textsf{spring}, was deleted in the commit
{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris
Beams on 20th January 2012, two years after it was
posted. 
% The latest version of Spring does not contain the file anymore.
\Cref{tab:stale_code_details} shows examples of the outdated online
clones on Stack Overflow. The table displays information of the clones
from both Stack Overflow and Qualitas side including the dates. We
summarise the changes that make the clones outdated into three types,
modified/added/deleted statements (\textit{S}), file deletion
(\textit{D}), and method rewriting (\textit{R}), along with the date
of change.

@@

\begin{table*}
	\centering
	\caption{Examples of the outdated QS online clones}
	\label{tab:stale_code_details}
	%\small
	%\resizebox{2\columnwidth}{!}{%
		\begin{tabular}{l|l|l|l|p{4.7cm}|r|r|l|c|l}
		 \hline
		 \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
		 \hline
		 Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
		 \hline
		 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
		 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
		 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
		 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
		 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
		 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
		 \hline 
		 \multicolumn{10}{l}{{\footnotesize * \textit{S}=modified/added/deleted statements, \textit{D}=file deletion,  \textit{R}=method rewriting}}
		\end{tabular} %
	%}
\end{table*}

@@

\begin{table}[]
	\centering
	\caption{License mapping of the online clones (file-level) in
          QS, UD, and EX FIXME switch UD and EX}
	\label{tab:license_abc}
	\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{2cm}l|rrr}
		\hline
		Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & UD & EX \\
%		\hline
%		No license & No license & No license &  5 & 21 & 4 \\
		\hline
		Compatible & Apache2 & Apache2 &  0 & 1 & 0 \\
		License	& EPLv1 & EPLv1 &  1 & 1 & 0 \\
		& Sun (proprietary) & Sun (proprietary) & 0 & 0 & 1 \\
		& MIT-like & MIT-like & 0 & 0 & 1 \\
		& No license & CC BY-NC-SA &  0 & 0 & 5 \\
		& No license & No license &  5 & 21 & 4 \\
		\hline
		\multicolumn{3}{l|}{Total} &  6 & 23 & 11 \\
		\hline
	    Incompat. & BSD3 & GPLv2+ & 0 & 1 & 0 \\
		License	& No license & AGPLv3/3+ & 1 & 2 & 0 \\
		& No license & Apache-2 & 41 & 23 & 5 \\
		& No license & BSD3 & 3 & 28 & 4 \\
		& No license & CDDL or GPLv2 & 1 & 58 & 0 \\
		& No license & CDDLv1 & 0 & 0 & 1 \\
		& No license & EPLv1 & 7 & 10 & 0 \\
		& No license & GPLv2/2+/3+ & 2 & 32 & 62 \\
		& No license & LGPLv2/2.1+/3+ & 24 & 32 & 0 \\
		& No license & MPLv1.1 & 0 & 1 & 0 \\
		& No license & spdxBSD3 & 0 & 10 & 0 \\
		& No license & SPLv1 & 0 & 0 & 1 \\
		& No license & Unknown & 0 & 3 & 3 \\
		& spdxBSD3 & AGPLv3+ & 0 & 2 & 0 \\
		\hline
		\multicolumn{3}{l|}{Total} &  79 & 202 & 76 \\
		\hline
	\end{tabular} %
%}
\end{table}

@@

In our study, we reveal another possible situation of software
licensing issues caused by code cloned to Stack Overflow. We found
evidence that 112 pieces of code have been copied from Qualitas
projects to Stack Overflow as examples. Their status of accepted
answers increase their chances of being reused. Even though most of
the Qualitas projects came with a software license (shown in
\Cref{t:q_projects_license}), we found that the licensing information
were frequently missing after the code was copied to Stack
Overflow. The licensing terms on top of source code files are not
copied because usually only a small part of the file was
cloned. 
%If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.

>>>>

\begin{table}
	\centering
	\caption{Configurations of Simian and NiCad}
	\label{t:param_tuning}
%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{p{0.7cm}|p{2.4cm}|p{3.5cm}}
		\hline 
		Tool & Default (\textit{D}) & EvaClone (\textit{E}) \\
		\hline
		Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, \newline ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\ 
		\hline 
		NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=2500 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming,\newline literal abstraction \\
		\hline
	\end{tabular} %
%}
\end{table}

@@

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{3}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-5}
		& & \textit{L} & \textit{S} & \textit{G} & \\
		\hline 
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & \checkmark & 88 \\ 
		\hline
		\multicolumn{6}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
	\end{tabular} %
	%}
\end{table}

@@

Even choosing only the default configurations, the number of disagreed
clone pair candidates is still too large for manual inspection (67,570
for $S_D$ and 632,855 pairs for $N_D$). We applied three filters: clone
size, irrelevant methods, similarity threshold, and good/ok pairs. For
the \emph{clone size filter}, we raised the minimum clone size to 10 lines
since larger clones are more interesting, while smaller ones tend to
be false clones~\cite{Saini2016}.
% Since the 10--line threshold is already the default configuration for
% NiCad, this filter is applied to Simian only (Simian's default
% configuration has a minimum clone size of 6 lines).
%The \emph{irrelevant methods filter} removes clones of
%\verb|hashCode()| methods and getters/setters which are almost always
%false clones. 
The second filter, \emph{similarity threshold}, applies
only to NiCad clone pairs since Simian does not provide a similarity
configuration. The last filter, \emph{good/ok pairs}, removes the
clone pairs that already exist in the agreed clone sets.

As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the
results using clone size and gook/ok pairs. The
two filters reduced the number of $S_D$ clones to 17,801 pairs. We
filtered $N_D$ clones by additionally raising the similarity
threshold. We increased NiCad's similarity threshold from 70\% to 85\%
(by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15). We
tried varying the UPI from 70\% (default, 632,855 pairs), 80\%
(25,003 pairs), 85\% (185 pairs) and 90\% (83 pairs) and found that
85\% similarity provided the best balance in terms of the amount of
reported clones and precision for small clones. Using this filter
along with the other three filters, we reduced the number of $N_D$
clones to 88 pairs.

@@

\FIXME{Do you think we should report at this level or in more details 
	into $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, $S_E$--$N_E$??}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. For the 2,308 \textit{good} pairs, there are 92 Stack Overflow snippets
which are associated with 66 Qualitas projects. The 11,749 \textit{ok} 
pairs are clones between 136 Stack Overflow snippets and 39 Qualitas 
projects.

Moreover, for the disagreed pairs, we found 17,081 clone pairs reported by $S_D$
are clones between 471 Stack Overflow snippets and 76 Qualitas projects and 
88 $N_D$ clone pairs are clones between 77 Stack Overflow snippets and 29
Qualitas projects.

% FIXME
% However, as it is well known that the precision of clone detectors is
% not very good, it is clear that the above numbers may not be
% representative for real code clones and we ...

@@

%\FIXME{Why equals here but not hashcode? Why isn't it the same
%  irrelevant methods filter?}

We rely on a manual study to qualitatively investigate the patterns of
online code cloning. To achieve this, we classified all 31,946
selected clone pairs according to the process shown in
\Cref{fig:classification_process}.  Before performing the manual
classification, we created and used an automatic classifier 
to classify {\small\texttt{equals()}}, 
{\small\texttt{hashCode()}} and getters/setters. As shown in
\Cref{tab:online_clone_classification_results}, the automatic
classifier helped us classified and captured 28,314 clone pairs into
pattern \textbf{BP}.

@@

\begin{table}
	\centering
	\caption{Classifications of online clone pairs.}
	\label{tab:classification_good_o}
	%\small
	%\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|rrrr|rrr|r}
			\hline
			Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
			\hline
			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 4 & 11 & 111  & 7 & 2,172 & 2,308 \\
			\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 41 & 20 & 11,547 & 22 & 105 & 11,749 \\
			\multirow{1}{*}{$S_D'$} & 86 & 0 & 146 & 293 & 17,074 & 74 & 128 & 17,801 \\
			\multirow{1}{*}{$N_D'$} & 9  & 0  & 6 & 35 & 17 & 8 & 13 & 88 \\ 
			\hline
			Total & 112 & 0 & 197 & 359 & 28,749 & 111 & 2,418 & 31,946 \\ 
			\hline
		\end{tabular} 
	%}
\end{table}

@@

\textbf{To answer RQ2, we found that a large amount of the clone pairs
  between Stack Overflow and Qualitas projects are boiler-plate code
  (28,642) or accidental clones (2,525) with no evidence that the code
  has actually been copied. Nevertheless, we found 112 pairs that had
  strong evidences to be cloned from Qualitas to Stack Overflow and
  178 pairs were found to be cloned to Stack Overflow from external
  sources outside Qualitas projects.} 
%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}

@@

%\FIXME{You are using the complete number of pairs in a project instead
%  of the outdated pairs!!!}
 %Some of the clone pairs overlap with each other so we group them in the same row. 
We discovered 64 outdated online clone pairs out of 112 pairs. As
shown in \Cref{fig:outdated}, \textsf{spring}
have the highest number of 17 outdated pairs, followed by 7 from
\textsf{hibernate} and \textsf{hadoop}, and 6 from \textsf{junit}. Besides the example of
outdated code in the \textsf{hadoop}'s
{\small{\texttt{WritableComparator.java}}} shown in
\Cref{fig:before-after}, we also found a few outdated code elements
which contained a large amount of modifications. For example, the code
snippet in Stack Overflow post 23520731 is a copy of
{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code
has been heavily modified on 5 February 2016.

In the 64 outdated pairs, we found 5 ``dead'' snippets. These snippets
cannot be located in the latest version of the projects. For example,
the snippet in Stack Overflow post 3758110, a copy of
{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in
\textsf{spring}, was deleted in the commit
{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris
Beams on 20th January 2012, two years after it was
posted. 
% The latest version of Spring does not contain the file anymore.
\Cref{tab:stale_code_details} shows examples of the outdated online
clones on Stack Overflow. The table displays information of the clones
from both Stack Overflow and Qualitas side including the dates. We
summarise the changes that make the clones outdated into three types,
modified/added/deleted statements (\textit{S}), file deletion
(\textit{D}), and method rewriting (\textit{R}), along with the date
of change.

@@

\begin{table*}
	\centering
	\caption{Examples of the outdated QS online clones}
	\label{tab:stale_code_details}
	%\small
	\resizebox{2.1\columnwidth}{!}{%
		\begin{tabular}{l|l|l|l|p{5.1cm}|r|r|l|c|l}
		 \hline
		 \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
		 \hline
		 Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
		 \hline
		 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
		 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
		 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
		 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
		 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
		 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
		 \hline 
		 \multicolumn{10}{l}{{\footnotesize * \textit{S}=modified/added/deleted statements, \textit{D}=file deletion,  \textit{R}=method rewriting}}
		\end{tabular} %
	}
\end{table*}

@@

\begin{table}[]
	\centering
	\caption{License mapping of the online clones (file-level) in
          QS, UD, and EX}
	\label{tab:license_abc}
	\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{2cm}l|rrr}
		\hline
		Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
		\hline
		Compatible & Apache2 & Apache2 &  0 & 0  & 1\\
		License	& EPLv1 & EPLv1 &  1 & 0 & 1\\
		& Sun (proprietary) & Sun (proprietary) & 0 & 1 & 0\\
		& MIT-like & MIT-like & 0 & 1 & 0\\
		& No license & CC BY-NC-SA & 0 & 5 & 0 \\
		& No license & No license & 5 & 4 & 21 \\
		\hline
		\multicolumn{3}{l|}{Total} & 6 & 11 & 23 \\
		\hline
	    Incompat. & BSD3 & GPLv2+ & 0 & 0 & 1 \\
		License	& No license & AGPLv3/3+ & 1 & 0 & 2 \\
		& No license & Apache-2 & 41 & 5 & 23 \\
		& No license & BSD3 & 3 & 4 & 28 \\
		& No license & CDDL or GPLv2 & 1 & 0 & 58 \\
		& No license & CDDLv1 & 0 & 1 & 0 \\
		& No license & EPLv1 & 7 & 0 & 10 \\
		& No license & GPLv2/2+/3+ & 2 & 62 & 32 \\
		& No license & LGPLv2/2.1+/3+ & 24 & 0 & 32 \\
		& No license & MPLv1.1 & 0 & 0 & 1 \\
		& No license & spdxBSD3 & 0 & 0 & 10 \\
		& No license & SPLv1 & 0 & 1 & 0 \\
		& No license & Unknown & 0 & 3 & 3 \\
		& spdxBSD3 & AGPLv3+ & 0 & 0 & 2 \\
		\hline
		\multicolumn{3}{l|}{Total} &  79 & 76 & 202 \\
		\hline
	\end{tabular} %
%}
\end{table}

@@

In our study, we reveal another possible situation of software
licensing issues caused by code cloned to Stack Overflow. We found
evidence that 112 pieces of code have been copied from Qualitas
projects to Stack Overflow as examples. Their status of accepted
answers increase their chances of being reused. Even though most of
the Qualitas projects came with a software license, we found that the licensing information
were frequently missing after the code was copied to Stack
Overflow. The licensing terms on top of source code files are not
copied because usually only a small part of the file was
cloned. 
%If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
